Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/mdp_background.tex
shroteinings

%MDP/SDM Background and Notation
gAn \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$. Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards. We assume without loss of generality that the range of all reward functions is normalized to $[0,1]$. The solution to an \ac{MDP} is called a policy, denoted $\pi: \mathcal{S} \mapsto \mathcal{A}$.

>>>>

%MDP/SDM Background and Notation
An \ac{MDP} is a problem representation for sequential decision making agents, represented by a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$. Here, $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is a finite set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s,a)$ denotes the reward received by the agent for executing action $a$ in state $s$; $\gamma \in [0, 1]$ is a discount factor that determines how much the agent prefers future rewards over immediate rewards. We assume without loss of generality that the range of all reward functions is normalized to $[0,1]$. The solution to an \ac{MDP} is called a policy, denoted $\pi: \mathcal{S} \mapsto \mathcal{A}$.
